Opening a Cold Case \\ {\large Investigating how Temperature Affects The Rate of Robberies}

### 2014-12-01 stat374/final_project.tex
Project written, homework 4 first three questions done

The main danger with a Poisson regression model, such as this, is that if the predicted mean function may not be able to capture fully how the mean varies. This would most likely be due to insufficient predictors being included. The result may be larger variance around the predicted mean than allowed for with the Poisson Distribution, invalidating the model. In this case, should the rest of the assumptions hold, a negative binomial regression can be used, which can be derived as a certain sum of Poisson distributions with varying means, as could be the case should the mean not be perfectly predicted by the predictors. This makes the Poisson model a particular example of a negative binomial, and a formal test can be used to decide if the additional parameter of a negative binomial is needed. Such a test might well have indicated that I should have used a negative binomial regression here, but given time constraints and a lack of familiarity, I simply went with the Poisson model. \par
Additionally, as with nonparametric models, a better tool for evaluating the fit of a particular specification of the model may have been cross validation rather than Akaike Information Criteria, since it gives a more direct estimate of over fitting. However, this model appears to under fit if anything, so cross validation may not have made such a large difference

\section{Nonparametric Model} 
To model this data with a nonparametric model, I ran separate local linear regressions on workdays and weekends/holidays, with each predicting the log of the sum number of robberies plus one with hour and temperature simultaneously. As with the Poisson model, I fit on an $80\%$ training subset. In fitting it, I used a Gaussian kernel, individual bandwidths for each point such that a constant portion of the total data was closer to the point than the bandwidth, and a relative scaling factor for the variables to determine which points were included in the neighborhood (essentially making a second component of the bandwidth for the second variable). These two values were chosen from a grid of values based on which resulting model had the lowest cross validation score. \par
The reasoning and justification for these choices are as such:
\begin{itemize}
    \item The kernel doesn't make a great deal of difference, so the choice was arbitrary. 
    \item Since I am particularly interested in how temperatures on the extreme edge of my data effect the robbery rate, I need a model with low boundary bias, making a local linear fit superior to a simpler kernel regression.
    \item Predicting log robberies nicely constrains the prediction to positive counts, which is what it should be in the real world.
    \item As the initial plots have shown, there seem to be fairly distinct trends between workdays and not workdays, so two separate models seemed more appropriate than one.
    \item Also as observed earlier, the relationship between temperature and robberies doesn't seem constant by time of day, so it would likely be insufficient to model it separately, as would be the result from a general additive model that included separate local linear models for hour and temperature
    \item The observations are not equally spaced out over their range, so one bandwidth for all the points wouldn't smooth enough on the extremes or too much in the middle. Instead, by dictating the bandwidth such it defined a neighborhood with a set number of neighbors, the amount of smoothing was comparable across the data points.
    \item Including a scaling factor for the second variable is essential, since the units of the two variables aren't comparable.
\end{itemize} \par
With this model, I am only really relying on two assumptions. First, the number or robberies as a particular time and temperature is related to the number of robberies at close time and temperatures, which is obvious. Second, I am assuming the true function is sufficiently smooth that some kind of linear fit in a  neighborhood can be used to give a reasonable prediction. If, for instance, the function had peaks and troughs more often than I had data, this method would fall apart. However, this seems unlikely from observing the data. \par
The parameters
\begin{figure}[h]
    {\bf Figure 5} \\
    \includegraphics[width=9cm]{final_project/ll_w_contour_fill}
    \includegraphics[width=9cm]{final_project/ll_nw_contour_fill}
\end{figure}
\begin{figure}[h]
    {\bf Figure 6} \\
    \includegraphics[width=9cm]{final_project/ll_w_ci}
    \includegraphics[width=9cm]{final_project/ll_nw_ci}
\end{figure}

\end{document}

>>>>

The main danger with a Poisson regression model, such as this, is that if the predicted mean function may not be able to capture fully how the mean varies. This would most likely be due to insufficient predictors being included. The result may be larger variance around the predicted mean than allowed for with the Poisson Distribution, invalidating the model. In this case, should the rest of the assumptions hold, a negative binomial regression can be used, which can be derived as a certain sum of Poisson distributions with varying means, as could be the case should the mean not be perfectly predicted by the predictors. This makes the Poisson model a particular example of a negative binomial, and a formal test can be used to decide if the additional parameter of a negative binomial is needed. Such a test might well have indicated that I should have used a negative binomial regression here, but given time constraints and a lack of familiarity, I simply went with the Poisson model. \par
Additionally, as with nonparametric models, a better tool for evaluating the fit of a particular specification of the model may have been cross validation rather than Akaike Information Criteria, since it gives a more direct estimate of over and under fitting.

\section{Nonparametric Model} 
To model this data with a nonparametric model, I ran separate local linear regressions on workdays and weekends/holidays, with each predicting the log of the sum number of robberies plus one with hour and temperature simultaneously. As with the Poisson model, I fit on an $80\%$ training subset. In fitting it, I used a Gaussian kernel, individual bandwidths for each point such that a constant portion of the total data was closer to the point than the bandwidth, and a relative scaling factor for the second variable (this effectively stretches or shrinks the kernel in one direction). These two values were chosen from a grid of values based on which resulting model had the lowest cross validation score. As well, the hour span was expanded to include the previous and next day's data, so there should be no boundary bias towards the beginning and end of days.\par
The reasoning and justification for these choices are as such:
\begin{itemize}
    \item The kernel doesn't make a great deal of difference, so the choice was arbitrary. 
    \item Since I am particularly interested in how temperatures on the extreme edge of my data effect the robbery rate. This necessitates a need a model with low boundary bias along the temperature range, making a local linear fit superior to a simpler kernel regression. Higher polynomial fits on the other hand make it increasingly difficult to fit the model well.
    \item Predicting log robberies nicely constrains the prediction to positive counts, which is what it should be in the real world.
    \item As the initial plots have shown, there seem to be fairly distinct trends between workdays and not workdays, so two separate models seemed more appropriate than one. 
    \item Also as observed earlier, the relationship between temperature and robberies doesn't appear constant by time of day, so it would likely be insufficient to model it separately, as would be the result from a general additive model that included separate local linear models for hour and temperature. In this case, there is a sufficient amount of data to still have a reasonable degree of accuracy, so the curse of dimensionality is not prohibitive.  
    \item The observations are not equally spaced out over their range, so one bandwidth for all the points wouldn't smooth enough on the extremes or too much in the middle. Instead, by dictating the bandwidth such that it defined a neighborhood with a fixed number of neighbors, the amount of smoothing was comparable across the data points.
    \item Including a scaling factor for the second variable is essential, since the units of the two variables aren't comparable.
\end{itemize} \par
With this model, I am only really relying on two assumptions. First, the number or robberies as a particular time and temperature is related to the number of robberies at close time and temperatures, which is obvious. Second, I am assuming sufficient smoothness to achieve convergence of the estimates. \par
    {\bf Figure 5} \\
    \includegraphics[width=9cm]{final_project/ll_w_contour_fill}
    \includegraphics[width=9cm]{final_project/ll_nw_contour_fill}
\FloatBarrier
The predictions of the models can be seen in the contour plots of Figure 5. It is important to note that with less data, bandwidths for the weekend/holiday model were chosen to include a larger portion of the data, and also that the scale was such that this model averaged more strongly over temperature than hour as compared to the workday model. This model seems to very clearly portray the patterns we have seen before. Peak crime on workdays is highest in the evening, with the main peak later and a second, smaller and earlier, peak developing when the temperature is higher. Also, the afternoon and evening crime rate does fall off as the temperature increases beyond a point. On non-workdays, the peak is in the earliest hours of the morning, and keeps increasing with the temperature. However, the prediction for the highest temperatures should be taken with a grain of salt; their is little if any data where temperatures actually reach that high at that hour of the day.
\FloatBarrier

\begin{figure}[h]
    {\bf Figure 6} \\
    \includegraphics[width=9cm]{final_project/ll_w_ci}
    \includegraphics[width=9cm]{final_project/ll_nw_ci}
\end{figure}
Evaluating the confidence of the fits, as seen in Figure 6, we see a much more nuanced picture for workdays than we saw from the Poisson model. It should be noted that the confidence intervals are based on local estimates of variance, necessitated by the variable bandwidth. This model is quite certain that the peak crime rate at $6$pm on workdays occurs when the temperature is between 30 and 50 degrees, and falls off afterwards, as opposed to the monotonic relationship predicted by the Poisson model. It also has a large amount of confidence there is a true increase in crime in the early morning, though as I noted, at high temperatures there is much more uncertainty. With much more smoothing, particularly over temperature, in the weekend/holiday model, its results look similar to the Poisson models. \par
It seems safe to say this model is the strongest non-parametric regression for this subject. Alternate linear smoothers and generalized additive models were discussed earlier. Monotonicity with hour or temperature doesn't seem to hold, nor does convexity/concavity, so models making those assumptions aren't appropriate. This series doesn't have the quickly varying features that would necessitate a procedure like wavelet regression. However, what could be quite a good alternate approach is to not have aggregated robbery counts, and fit a density estimate to the data. This could be scaled by how often different temperature and hour combinations occurred to give relative rates of robbery. This approach has the advantage of preserving more information about the time a crime occurs, but is computationally more intensive (with more data points), and doesn't easily admit a comparable parametric model.

\section{Discussion} 
Comparing the two models just based on performance, the nonparametric model wins, though they both do fairly well. I calculated the root mean squared log error for each model over the $20\%$ test subset that wasn't used to train the models. The local linear model had a RMSLE of $.510$, while the Poisson model had a RMSLE of $.529$. By comparison, an unbiased estimate where the mean at each temperature/hour combination in the training data was taken had a RMSLE of $.563$, so both models are a meaningful improvement. \par
Subjectively, they both picked up mostly the same trends. The only notable distinction was in how they treated the late afternoon and early evening period, with the Poisson model apparently failing to capture the non-monotone trend. However, by including more and varied predictors (from interactions, splines, transformations, etc.), one can get and arbitrary degree of flexibility. Choosing a sufficient set of predictors is a slow process to do manually though, making it easier to just start with a non-parametric method which has arbitrary flexibility built in. One could meet halfway between the methods with a nonparametric model fit with local likelihood, since the assumption that the error is Poisson or negative binomial distributed seems appropriate. \par
In terms of interpretation, both are pretty convincingly show that the rate of robberies varies with temperature, generally increasing with it. Causation is quite unclear though; temperature is highly correlated with a number of other seasonal factors. One could reasonably expect the rate of robberies to vary with school holidays, daylight hours, or just the time of the year irrespective of season. By including all these factors in a model, it would likely be highly predictive, but the high collinearity can be expected to make it hard to attribute changes to just one factor, modeled parametrically or not. Appropriately modeling these effects would be the most important extension of the current model. \par
There are a number of other areas where this model could be expanded though. There is a great wealth of geographic data in the Chicago crime database, and there is likely a great deal of heterogeneity in the baseline rate of robberies by geography, as well as the differences in the effect of weather on that rate. Different types of crime could also be investigated. Different attributes of the weather may also play a roll. I initially investigated the effect of precipitation on the robbery rate. The presence of precipitation, as showed in Figure 7, does seem to coincide with a small reduction in robberies, at least in during the late evening and early morning. This effect appears to vary a lot with the amount of precipitation, and there were relatively little data from when there was enough precipitation to have a meaningful effect. With the Poisson model, every version I tried which included precipitation in some form had an inferior AIC, so ultimately I decided not to model it, at least for now. Finally, there is slight asymmetry between the early morning and late evening predictions due to how the weekends are defined. Friday evening is likely more akin to a Saturday night, with more robberies, pushing up the late evening average of workdays as compared to the early mornings, while Sunday evening likely has the opposite effect on the Weekends/Holidays. A modified delineation between the two periods may have done away with this, improving the fit. There may be further clustering that could be preformed on the days as well. All these areas present opportunity for further refinement.

\begin{figure}[h]
    {\bf Figure 7} \\
    \includegraphics[width=9cm]{final_project/precip}
\end{figure}
\end{document}

### 2014-12-01 stat374/hw4.tex
Project written, homework 4 first three questions done

            \item[(c)] Let $c(x_n)$ be the concave sequence of points evaluated at points $x_n$, and let $s(x_n)$ be a corresponding convex sequence. I will attempt to show that if $s(x_n)$ is not linear, it can not be the best fit. We can break this problem down into three cases.
                \begin{itemize}
                    \item[case 1:] If $s(x_n)>c(x_n)$ for all $x$, then there is trivially a better fit $s(x_n)-c$, where $c$ is the minimum distance between the two sequences. This will reduce the problem to the next case.
                    \item[case 2:] $s(x_n)=c(x_n)$ for at least one $n$, but it is never the case $s(x_n)<c(x_n)$. Let $s(x_1)=c(x_1)$. Since $s$ and $c$ are respectively convex and concave, there exists a line passing through $s(x_1)=c(x_1)$ such that $s(x_n)\geq l(x_n) \geq c(x_n) \, \forall n$. If $s(x_n)$ isn't itself a line, then there will be a $n$ for which their is strict inequality on the left hand side, making $l$ a superior fit to $s$.
                    \item[case 3:] $s(x_n)<c(x_n)$ for some $n$. Let us flesh
out $s(x_n)$ and $c(x_n)$, such that $s(x)$ and $c(x)$ are piecewise linear
functions connecting the points of the respective sequences. These functions
are necessarily also convex and concave respectively. We once again have three
cases:
                        \begin{itemize}
                            \item[case 3.1:] If $s(x)$ and $c(x)$ never intersect, a shift as in case 1 will achieve a superior fit and reduce the problem to the next case.
                            \item[case 3.2:]  
                            \item[case 3.3:] If they $s(x)$ and $c(x)$ intersect at multiple points, we can choose two intersection points $a<b$. Let $l$ be the line passing through them. It is a secant line for both $s$ and $c$, so by their respective convexity/concavity, $c(x)\geq l(x) \geq s(x)$ on $[a,b]$ and $c(x)\leq l(x) \leq s(x)$ elsewhere. Thus, if $c(x)\neq l(x)$ for some $x$, then $l$ is a superior fit to the function $s$. Since $s$ and $c$ are linear between the $x_n$, this can only arise if $s(x_n)\neq l(x_n)$ for some $n$, making $l(x_n)$ a superior fit to $c(x_n)$.

                        \end{itemize}
                \end{itemize}
        \end{itemize}
    \item[2.]
        I have computed the mean squared error for each of the methods:
        \FloatBarrier
        \input{hw4_2} 
        \FloatBarrier
        \begin{itemize}
            \item[(a)]
                At a low level of noise, the wavelet methods all preform better than the local linear model. With low noise, their ability to accurately match the fine features of the Doppler function win out. None of them preform terribly though. On the other hand, once the noise increases, the James Stein and Universal Threshold methods get worse much quicker than Sure Shrink and local linear, which are comparatively much better. This is likely since it becomes harder to distinguish feature from noise. In both cases, the James Stein is worse than the Universal Threshold, and Local Linear loses out to Sure Shrink. As the graphs note the distinction between local linear regression and Sure Shrink are hard to pick out by eye  \\
                \includegraphics[width=9cm]{hw4/2_ab_pt1} 
                \includegraphics[width=9cm]{hw4/2_ab_pt01} \\
            \item[(b)]
                On the other hand, once there are occasional spikes in the variance, the local linear model preforms the best. As the graph shows, it preforms more smoothing on the occasional spikes than the Sure Shrink, which likely has them identified as true features.
                \begin{center}
                    \includegraphics[width=9cm]{hw4/2_ab_bimodal} 
                \end{center}
    \item[3.]

>>>>

            \item[(c)] Let $c(x_n)$ be the concave sequence of points evaluated at points $x_n$, and let $s(x_n)$ be a corresponding convex sequence. I will attempt to show that if $s(x_n)$ is not linear, it is superseded by some linear function. We can break this problem down into three cases.
                \begin{itemize}
                    \item[case 1:] If $s(x_n)>c(x_n)$ for all $x$, then there is trivially a better fit $s(x_n)-c$, where $c$ is the minimum distance between the two sequences. This improved fit is of the next case, so if there is a superseding linear fit for it, there is one for this case as well.
                    \item[case 2:] $s(x_n)=c(x_n)$ for at least one $n$, but it is never the case $s(x_n)<c(x_n)$. Let $s(x_1)=c(x_1)$. Since $s$ and $c$ are respectively convex and concave, there exists a line passing through $s(x_1)=c(x_1)$ such that $s(x_n)\geq l(x_n) \geq c(x_n) \, \forall n$. If $s(x_n)$ isn't itself a line, then there will be a $n$ for which their is strict inequality on the left hand side, making $l$ a superior fit to $s$.
                    \item[case 3:] $s(x_n)<c(x_n)$ for some $n$. Let us flesh out $s(x_n)$ and $c(x_n)$, such that $s(x)$ and $c(x)$ are piecewise linear functions connecting the points of each sequence. These functions are necessarily also convex and concave respectively. We once again have three cases:
                        \begin{itemize}
                            \item[case 3.1:] If $s(x)$ and $c(x)$ never intersect, a shift as in case 1 will achieve a superior fit and reduce the problem to the next case.
                            \item[case 3.2:] If $s(x)$ and $c(x)$ intersect exactly once, we can replace $s(x_n)$ with $s(x_n)+c$ for $n$ such that $s(x_n)<c(x_n)$, where $c$ is the minimum distance between the sequences on this set. This action will preserve convexity while creating an improved fit (the distance is strictly reduced), and reduces this case to the next case. 
                            \item[case 3.3:] If they $s(x)$ and $c(x)$ intersect at multiple points, we can choose two intersection points $a<b$. Let $l$ be the line passing through them. It is a secant line for both $s$ and $c$, so by their respective convexity/concavity, $c(x)\geq l(x) \geq s(x)$ on $[a,b]$ and $c(x)\leq l(x) \leq s(x)$ elsewhere. Thus, if $c(x)\neq l(x)$ for some $x$, then $l$ is a superior fit to the function $s$. Since $s$ and $c$ are linear between the $x_n$, this can only arise if $s(x_n)\neq l(x_n)$ for some $n$, making $l(x_n)$ a superior fit to $c(x_n)$.
    \item[2.]
        I have computed the mean squared error for each of the methods:
        \FloatBarrier
        \input{hw4_2} 
        \FloatBarrier
        \begin{itemize}
            \item[(a)]
                At a low level of noise, the wavelet methods all preform better than the local linear model. With low noise, their ability to accurately match the fine features of the Doppler function win out. None of them preform terribly though. On the other hand, once the noise increases, the James Stein and Universal Threshold methods get worse much quicker than Sure Shrink and local linear, which are comparatively much better. This is likely since it becomes harder to distinguish feature from noise. In both cases, the James Stein is worse than the Universal Threshold, and Local Linear loses out to Sure Shrink. As the graphs note the distinction between local linear regression and Sure Shrink are hard to pick out by eye  \\
                \includegraphics[width=9cm]{hw4/2_ab_pt1} 
                \includegraphics[width=9cm]{hw4/2_ab_pt01} \\
            \item[(b)]
                On the other hand, once there are occasional spikes in the variance, the local linear model preforms the best. As the graph shows, it preforms more smoothing on the occasional spikes than the Sure Shrink, which likely has them identified as true features.
                \begin{center}
                    \includegraphics[width=9cm]{hw4/2_ab_bimodal} 
                \end{center}
    \item[3.]
        \begin{itemize}
            \item[(a)]
                I have plotted out all of the fits in the graph below. The isotonic regression provides a good fit only over through day 25 or so, when the observed values cease to be monotone. After that, the shorter fits do a reasonable job over the middle part, which is essentially flat. However, the more data the regression is fit on where the trend actually seems to be decreasing, the worse the regression preforms. Assuming the error terms are symmetrically distributed, one would expect at worst $50\%$ of the observations to fall below the actual series. One could thus generate a test statistic based on how the number of times, as the function is generated step by step, the function is forced to drop in response to a lower observed value within a particular range. This statistic would be approximately binomially distributed (though there is additional uncertainty due to the function being noisy), and a critical value could be generated from this to determine whether the range isn't monotone.
                \begin{center}
                    \includegraphics[width=9cm]{hw4/3_a} 
                \end{center}
            \item[(b)] 
                The series of local linear fits are generally pretty good. However, as they are fit in increasingly noisy parts of the data, they have a greater amount of uncertainty, since the confidence interval is fit with a constant variance assumption.
                    \includegraphics[width=9cm]{hw4/3_b25day} 
                    \includegraphics[width=9cm]{hw4/3_b50day}  \\
                    \includegraphics[width=9cm]{hw4/3_b75day} 
                    \includegraphics[width=9cm]{hw4/3_b85day}  \\
                    \includegraphics[width=9cm]{hw4/3_b171day} 
            \item[(c)]
                The Haar wavelet fit is below. Its fit is comparable on the relatively smooth portion of the series. However, in the noisy section to the end, it mostly clings to the large fluctuations in the data, while the others averaged them out in one way or another. Since these fluctuations are due to the small number of surviving flies, rather than a reflection of the true rate, this constitutes a worse fit.
                \begin{center}
                    \includegraphics[width=9cm]{hw4/3_c} 
                \end{center}
                {\textbf My Code:}
               \lstinputlisting[firstline=181,lastline=210]{hw4.R}
            \item[(d)]
                The Daubechies wavelet fit, much like the Haar, clings to closely to the observed data when the noise accounts for large swings, but otherwise has a similar, somewhat smoother, fit over the relatively calm part of the data.
                \begin{center}
                    \includegraphics[width=9cm]{hw4/3_d} 
                \end{center}

        \end{itemize}
    \item[4.]
        \begin{itemize}
            \item[(a)]
                \begin{align*}
                    \E(\mu \vert \mathcal{D}_n) &= \int_{\R^d} \mu  p(\mu \vert \mathcal{D}_n) \, d\mu \\
                    \E(\mu \vert \mathcal{D}_n) &= \frac{\int_{\R^d} \mu  p(\mathcal{D}_n \vert \mu) \pi(\mu) \, d\mu}{\int_{\R^d}p(\mathcal{D}_n \vert \mu) \pi(\mu) \, d\mu} \\
                    \E(\mu \vert \mathcal{D}_n) &= \frac{\int_{\R^d} \mu \prod_{i=1}^n \frac{1}{2\pi}e^{-\|x_i-\mu\|^2}  \, d\mu}{\int_{\R^d}\prod_{i=1}^n\frac{1}{2\pi} e^{-\|x_i-\mu\|^2} \, d\mu}  \\
                    \E(\mu \vert \mathcal{D}_n) &= \frac{\int_{\R^d} \mu \frac{1}{2\pi} e^{-\sum_{i=1}^n\|x_i-\mu\|^2}  \, d\mu}{\int_{\R^d}\frac{1}{2\pi}e^{-\sum_{i=1}^n\|x_i-\mu\|^2} \, d\mu}  \\
                    \E(\mu \vert \mathcal{D}_n) &= \frac{\int_{\R^d} \mu \frac{1}{2\pi} e^{-n\|\mu-\sum_{i=1}^n\frac{x_i}{n}\|^2 -n\left(\sum_{i=1}^n\frac{\|x_i\|^2}{n}-\left\|\sum_{i=1}^n\frac{x_i}{n}\right\|^2\right)}  \, d\mu}{\int_{\R^d}\frac{1}{2\pi}e^{-n\|\mu-\sum_{i=1}^n\frac{x_i}{n}\|^2 -n\left(\sum_{i=1}^n\frac{\|x_i\|^2}{n}-\left\|\sum_{i=1}^n\frac{x_i}{n}\right\|^2\right)} \, d\mu}  \\
                    \E(\mu \vert \mathcal{D}_n) &= \frac{\int_{\R^d} \mu \frac{1}{2\pi} e^{-n\|\mu-\sum_{i=1}^n\frac{x_i}{n}\|^2}  \, d\mu}{\int_{\R^d}\frac{1}{2\pi}e^{-n\|\mu-\sum_{i=1}^n\frac{x_i}{n}\|^2} \, d\mu}  \\
                    \E(\mu \vert \mathcal{D}_n) &= \int_{\R^d} \mu \frac{1}{2\pi} e^{-n\|\mu-\sum_{i=1}^n\frac{x_i}{n}\|^2}  \, d\mu\\
                    \E(\mu \vert \mathcal{D}_n) &= \sum_{i=1}^n\frac{x_i}{n}\\
                \end{align*}
        \item[(b)]
                Let \(y_i=\|x_i\|^2\) and \(\mathcal{H}_n={y_1,...,y_n}\). Since each component of each $x_i$  is independent of the others (because there is $0$ covariance and the distribution is multivariate normal), we may conclude that the $y_i$ have a $\chi^2$ distribution with $d$ degrees of freedom and a noncentrality parameter of $\|\mu\|^2$. Thus,
            \begin{align*}
                p(\theta\vert \mathcal{H}_n) &= \frac{p(\mathcal{H}_n \vert \theta)p(\theta)}{p(\mathcal{H}_n)} \\
                p(\theta\vert \mathcal{H}_n) &= \frac{\prod_{i=1}^n p(y_i \vert \theta)\int_{\R^d} p(\theta \vert \mu) p(\mu) d\mu}{\int_{\R^d}p(\mathcal{H}_n\vert \mu)p(\mu)} \\
                p(\theta\vert \mathcal{H}_n) &= \frac{\prod_{i=1}^n p(y_i \vert \theta)\int_{\R^d} I_{\{\|x\|^2=\theta\}}(\mu) d\mu}{\int_{\R^d}\prod_{i=1}^n p(y_i \vert \theta) d\mu)} \\
            \end{align*}
        \end{itemize}
    \item[5.]
        \begin{itemize}
            \item[(a)]
                \begin{align*}
                    \sum_{j=1}^n w_j &= V_1 + \sum_{j=2}^n V_j \prod_{i=1}^{j-1}(1-V_i) \\
                    \sum_{j=1}^n w_j &= 1 - \prod_{j=1}^{n}(1-V_i) \\
                    \sum_{j=\infty}^n w_j &= 1 - \prod_{j=1}^{\infty}(1-V_j) \\
                \end{align*}
